### 2015-06-10 adp.tex
Refining the meaning of DP, making the intro more precise

%!TEX root =  autocontgrlp.tex
\section{Approximate Dynamic Programming}
\emph{Curse-of-dimensionality} is a term used to denote the fact that the number of states and computational costs grow exponentially in the dimensions of the state space. \todoc{This itself won't be a curse, would it be? The problem is that the computation cost also grows exponentially. Note that we never defined what we mean by state variables.}
Most MDPs arising in practical applications suffer from the curse, i.e., have large number of states and it is difficult to compute $J^*/J_u\in \R^n$ exactly in such scenarios. Approximate dynamic programming (ADP) \cite{lspi,lspe,ALP,wang2014approximate} methods compute an approximate value function $\tilde{J}$ instead of $J^*/J_u$. In order to tackle the curse, ADP methods resort to dimensionality reduction by parametrizing the value function and/or the policy. Value-function based ADP methods form an important subclass of ADP methods whose brief overview is given below.

\subsection{Value-Function based ADP}
In the value-function based ADP schemes a parametrized family is chosen and the approximate value-function $\tilde{J}$ is picked from the chosen parametrized class.
Once the approximate value function $\tilde{J}$ is computed, a sub-optimal policy $\tilde{u}$ can be obtained as the one-step greedy policy with respect to $\tilde{J}$ by making use of \eqref{subpol}.
The following lemma characterizes the degree of sub-optimality of the greedy policy $\tilde{u}$.
\begin{lemma}\label{subopt}
Let $\tilde{J}$ be the approximate value function and $\tilde{u}$ be as in \eqref{subpol}, then 
\begin{align}
||J^*-J_{\tilde{u}}||_\infty \leq \frac{2}{1-\alpha}||J^*-\tilde{J}||_\infty\,.
\end{align}
\end{lemma}
The quality of any ADP method depends on the approximation guarantees it offers for the quantities $||J^*-\tilde{J}||$ and $||J^*-J_{\tu}||$, where $||\cdot||$ is an appropriate norm. The term  $||J^*-\tilde{J}||$ denotes the error in prediction and $||J^*-J_{\tu}||$ denotes the loss in performance resulting from the sub-optimal policy $\tu$ with respect to the optimal policy $u^*$. Of the two error terms, $||J^*-J_{\tu}||$ is more important because ultimately we are interested in coming up with a useful policy. In the context of ADP methods, the control and prediction problems are said to be addressed when the error terms $||J^*-\tilde{J}||$ and $||J^*-J_{\tu}||$ are bounded by ``small'' constants.

>>>>

%!TEX root =  autocontgrlp.tex
\section{Approximate Dynamic Programming}
In practical problems, often the states are best described as multi-dimensional tuples.
In this context, the term \emph{curse-of-dimensionality} refers to the fact that the number of states
	grows exponentially as a function of the number of dimensions
	and thus solution methods whose computation cost grows at least linearly with the size of the state space
	quickly become intractable.
%Most MDPs arising in practical applications suffer from the curse, i.e., have large number of states and it is difficult to compute $J^*/J_u\in \R^n$ exactly in such scenarios. 
Approximate dynamic programming (ADP) \cite{lspi,lspe,ALP,wang2014approximate} methods compute an approximate value function $\tilde{J}$ instead of $J^*/J_u$. 
In order to tackle the curse, ADP methods resort to dimensionality reduction by parametrizing the value function and/or the policy. Value-function based ADP methods form an important subclass of ADP methods whose brief overview is given below.

\subsection{Value-Function based ADP}
In the value-function based ADP schemes a parametrized family is chosen and the approximate value-function $\tilde{J}$ is picked from the chosen parametrized class.
Once the approximate value function $\tilde{J}$ is computed, a sub-optimal policy $\tilde{u}$ can be obtained as the one-step greedy policy with respect to $\tilde{J}$ by making use of \eqref{subpol}.
The following lemma characterizes the degree of sub-optimality of the greedy policy $\tilde{u}$. \todoc{Add citation.}
\begin{lemma}\label{subopt}
Let $\tilde{J}$ be the approximate value function and $\tilde{u}$ be as in \eqref{subpol}, then 
\begin{align}
||J^*-J_{\tilde{u}}||_\infty \leq \frac{2}{1-\alpha}||J^*-\tilde{J}||_\infty\,.
\end{align}
\end{lemma}
The quality of any ADP method depends on the approximation guarantees it offers for the quantities $||J^*-\tilde{J}||$ and $||J^*-J_{\tu}||$, where $||\cdot||$ is an appropriate norm. The term  $||J^*-\tilde{J}||$ denotes the error in prediction and $||J^*-J_{\tu}||$ denotes the loss in performance resulting from the sub-optimal policy $\tu$ with respect to the optimal policy $u^*$. Of the two error terms, $||J^*-J_{\tu}||$ is more important because ultimately we are interested in coming up with a useful policy. In the context of ADP methods, the control and prediction problems are said to be addressed when the error terms $||J^*-\tilde{J}||$ and $||J^*-J_{\tu}||$ are bounded by ``small'' constants.
